Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-28 main-sketch.tex
removed some figures

In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
The results show that when the data size
increases, the average errors of
$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
i.e with size less 650 in the case of Beta-Binomial systems,
the Laplace mechanisms outperforms the exponential mechanisms,
but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
we considered data sets of the order of 15 thousands elements,
the exponential mechanisms outperforms the Laplace mechanism.
Similar experimental results were obtained for the Dirichlet-Multinomial system.

>>>>

In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
The results show that when the data size
increases, the average errors of
$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
i.e with size less 650 in the case of Beta-Binomial systems,
the Laplace mechanisms outperforms the exponential mechanisms,
but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
we considered data sets of the order of 15 thousands elements,
the exponential mechanisms outperforms the Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
too high run time of the algorithm.
